---
title: "Multiple Traits"
output: html_document
---
## Relationship between multiple traits

### What is the relationship between body mass and flipper length in penguins in this dataset?
```{r, echo=FALSE, message=FALSE, warning=FALSE}
penguins %>%
  ggplot(mapping = aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point() +
  geom_smooth(method = "lm")
```

*Flipper length increases with body mass. There is a postive relationship between body mass and flipper length.*

### Does this relationship differ between species?
```{r, echo=FALSE, message=FALSE, warning=FALSE}
penguins %>%
  ggplot() +
  geom_point(mapping = aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  facet_wrap(~species, nrow=3)
```

*Flipper length displays a slight upward trend as body mass increases in all penguin species.*

### Given the same body mass, which species of penguins tend to have the longest flippers?

*Gentoo penguin species tend to have longer flippers on average.*

<br>
