---
title: "Single Trait"
output: html_document
---
```{r message=FALSE, warning=FALSE, include=FALSE}
library(palmerpenguins) #install.packages("palmerpenguins")
library(tidyverse)
```
## Single trait distribution

### What is the lowest and highest bill lengths do penguins in this dataset have? 

```{r message=FALSE, warning=FALSE, include=FALSE}
summary(penguins)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
penguins %>%
  ggplot() +
  geom_density(mapping = aes(x = bill_length_mm, fill=species), alpha=0.5)
```

*The lowest bill length is 32.10 mm and the highest bill length is 59.60 mm.*

### Do different species have different bill lengths? How much do they overlap?
```{r, echo=FALSE, message=FALSE, warning=FALSE}
penguins %>%
  ggplot() +
  geom_histogram(mapping = aes(x = bill_length_mm, fill=species)) +
  facet_wrap(~species, nrow=3)
```

*Bill length differs by species, `Gentoo` and `Chinstrap` having the largest and `Adelie` having the smallest.`Gentoo` and `Chinstrap` have very similar bill lengths, ranging from ~40 mm to ~60 mm.*
